---
title: "Aides Drug"
author: "Yolanda Landeros!"
date: "May 4 2019"
output: 
  html_document:
    number_section: true
    toc: true
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(dplyr)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avastIV = filter(avast, Ivdrug=='user')
avastLBGT = filter(avast, LBGT=='yes')
avastFsex = filter(avast, sex=='F')
avastMsex = filter(avast, sex=='M')
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new prevention aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation.

The first question is this: does abacavirinol have any affect on wheter one contracts AIDS or not?

$H_0:$ avacabirinol has no effect on wheather one contracts AIDS or not.  
$H_1:$ avacabirinol has an effect on wheter on contracts. AIDS or not.

The reamining questions are: does abacavirinol have a different effect base on gender.

$H_0:$ gender has no effect on whether abacavirinol offers any protection against contracting AIDS.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be
used!-->

For each hypothesis test the graphical summary will be a bar plot, the numerical summary will be a cross tabulation, and a chi-squared test will be used for the inferential results. 

#Results 

Is the vaccine effective in the general population.

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results


### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+treatment, data=avast, type='percent')
```


This bar chart shows that persons that recieved the drug got aids it appears is smaller then those that got the placebo.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
genTable = xtabs(~treatment+infected, data=avast)
print(genTable)
rowPerc(genTable)
colPerc(genTable)
```




The table shows the amount of people who got the drug or placebo and the resutls. the vaccine can expose you to aids.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(~treatment+infected, data=avast)
```
The P value is 0.
Since the p value is 0 we can conclude that theh treamnet does  affect wether you contratct aids or not.
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
OVERALL Null hypothesis is that the vaccine has no effect on the general infected population.
The p-value was 0,so we reject the null hypothesis which is smaller than .05. Because the response and explanatory values are categorical, the bar plot and chi-square test for independence.

#Results 


<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
Does gender effect the vacine effectiveness?

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+treatment, data=avastFsex, type='percent')
```
This bar chart shows the difference between male and female population that recieved the drug or placebo and the effectevness. 
The woman that received the drug had a high probability of having aids so it wouod be best if woman did not get the treatment.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
genTable = xtabs(~infected + treatment, data=avastFsex)
print(genTable)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research
question!-->
```{r}
chisqtestGC(~infected+treatment, data=avastFsex)
```
The woman that received the drug had a high probability of having aids so it wouod be best if woman did not get the treatment. But for men it does help if they receive the treatment. 
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
GENDER The results demonstrate that the vaccine is reasonably effective on the general population. Null hypothesis is that the vaccine has no effect on the general infected population.
The p-value was 0.0001 , so we fail to reject the null hypothesis which is smaller than .05. Because the response and explanatory values are categorical, the bar plot and chi-square test for independence.


#Results drug users

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
Will being an IV drug user affect the effectivness of the vaccine?

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
```{r}
barchartGC(~infected+treatment, data=avastIV, type='percent')
```

This bar chart here shows that there is not a huge difference between the placebo and drug among LBGT population.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
genTable = xtabs(~treatment+Ivdrug, data=avast)
print(genTable)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisqtestGC(~treatment+Ivdrug, data=avast)
```
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
IV DRUG The results demonstrate that the vaccine is slightly less effective with IV drug users.
The null hypothesis was that IV Drug use had no effect on the effectiveness of the vaccine.
The p-value was 0.155 , so we fail to reject the null hypothesis which is greater than .05. Because the response and explanatory values are categorical, the bar plot and chi-squared test | test for independence.

#Results 

Does the sexual orientation make a difference in vaccine effectiveness.

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
```{r}
barchartGC(~infected+treatment, data=avastLBGT, type='percent')
```

The LGBT population should take the treatment because it signifacntly reduces aids infection


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->



```{r}
genTable = xtabs(~treatment+LBGT, data=avast)
print(genTable)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisqtestGC(~treatment+infected, data=avastLBGT)
```

The inferential results say that the LBGT community should take the vaccine because it will decrese their chances of contracting aids.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
LBGT The results demonstrate that the vaccine is not as effective on the LBGT population.
The null hypothesis was that sexual orientation does not effect the effectiveness of the vaccine.
The p-value was 0.0104, so we reject the null hypothesis which is smaller than .05. Because the response and explanatory values are categorical, the bar plot and chi-squared test | test for independence.
The vaccine looks like it is somewhat effective on the general population. It seems to be unaffected by gender or Sexual orientation. The testing indicates we reject the null hypotheses and accept that the vaccine appears to have some positive effect, which is slightly less for some subgroups including IV drug users.

  
